NIRCam Faint and Bright Flux Calibration Plan

### 2017-04-14 ms.tex
I made several more updates to the labels and description of the NIRCam sat/sens figure.

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.48\columnwidth]{nircam_wide_filters.png}
\includegraphics[width=.48\columnwidth]{calspec_and_new_clust.pdf}
\caption{{\it Left:} The NIRCam subarray saturation, full frame saturation and 10~$\sigma$ sensitivity limits for wide band imaging from \citet{gordon2011fluxplan2}. The three values are shown as upper, middle and lower limit error bars respectively. For comparison, three classes of JWST calibrators are shown: hot stars including white dwarfs (blue), A-type stars (green) and G-type stars (red).
Additional faint calibrators are needed to extend the sample from \citet{gordon2011fluxplan2} towards the faint limits of NIRCam.
{\it Right:} The new expected G2 V calibrators as compared to the faintest G-type star in the calibration plan.}\label{fig:JWStcalsWideF}
\end{figure}

>>>>

\begin{figure}[!hbtp]
\centering
%\includegraphics[width=.48\columnwidth]{nircam_wide_filters.png}
\includegraphics[width=.48\columnwidth]{calspec_and_new_clust.pdf}
\caption{{\it Left:} The NIRCam subarray saturation, full frame saturation and 10~$\sigma$ sensitivity limits for wide band imaging from \citet{gordon2011fluxplan2} in one hour. The three values are shown as upper, middle and lower limit error bars respectively. For comparison, three classes of JWST calibrators are shown: hot stars including white dwarfs (blue), A-type stars (green) and G-type stars (red).
Additional faint calibrators are needed to extend the sample from \citet{gordon2011fluxplan2} towards the faint limits of NIRCam.
Example G2~V \citet{castelli2004models} models are shown for stars expected in the three clusters NGC~6811, NGC~2420 and NGC~2506.
}\label{fig:JWStcalsWideF}
\end{figure}
